On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-27 docs/mvfits_paper/mvf.tex
misc updates

	\caption{ Spherical-spheroidal harmonic mixing coefficients. Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. (Top Left) Mixing coefficients for cases where $(\bar{\ell},\bar{m})=(\ell,m)$. The dashed horizontal intersects each curve at the Schwarzschild limit where $\jf=0$. (Top Right) Mixing coefficients where $(\bar{\ell},\bar{m})\neq(\ell,m)$. (Bottom Left and Right) Factional residuals for mixing coefficient fits. }

>>>>

	\caption{ Spherical-spheroidal harmonic mixing coefficients and percentage residual errors for spherical-spheroidal harmonic mixing coefficient fits. (\textit{Top Left}) Mixing coefficients for cases where $(\bar{\ell},\bar{m})=(\ell,m)$. The dashed horizontal intersects each curve at the Schwarzschild limit where $\jf=0$. (\textit{Top Right}) Mixing coefficients where $(\bar{\ell},\bar{m})\neq(\ell,m)$. (\textit{Bottom Left and Right}) Factional residuals for mixing coefficient fits. }
